checkData

### 2023-08-25 analysis/checkData.Rmd
Update checkData.Rmd

```{r}
d_articles <- d_articles %>%
  mutate(ppc_linked_final = case_when(
    exclusion_final == "EXCLUDE" ~ NA_character_, # if article is excluded, use NA
    sampleID == 'prominent' & article_id == '38' ~ ppc_linked_secondary,
    exclusion_final == "RETAIN" & exclusion_primary == "RETAIN" ~ ppc_linked_primary,
    exclusion_final == "RETAIN" & exclusion_secondary == "RETAIN" ~ ppc_linked_secondary,
    TRUE ~ "ERROR" # if none of the above, retain whatever is in this column already
  ))
```
```{r}
d_articles %>%
  count(exclusion_final,ppc_linked_final,sampleID)
```

>>>>

```{r}
d_articles <- d_articles %>%
  mutate(ppc_linked_final = case_when(
    exclusion_final == "EXCLUDE" ~ NA_character_, # if article is excluded, use NA
    sampleID == 'prominent' & article_id == '38' ~ ppc_linked_secondary,
    exclusion_final == "RETAIN" & exclusion_primary == "RETAIN" ~ ppc_linked_primary,
    exclusion_final == "RETAIN" & exclusion_secondary == "RETAIN" ~ ppc_linked_secondary,
    TRUE ~ "ERROR" # if none of the above, retain whatever is in this column already
  ))
```

After removing excluded articles, there should be

```{r}
d_articles %>%
  filter(exclusion_final == "RETAIN") %>%
  count(sampleID, coder_id_primary)
```
